%!TEX root = main.tex
\section{The Case of Multiple Target Parameters}
\label{append:mult}
  The fundamental idea behind the FMSC is to approximate finite-sample risk with asymptotic risk under local mis-specification.
  We can use the same idea when there are multiple target parameters: all we need to do is specify an appropriate risk function.
  Consider a generic weighted quadratic risk function of the form
  \[
    R(\widehat{\theta}_S,W) = E\left[ \left( \widehat{\theta}_S - \theta_0 \right)' W \left( \widehat{\theta} - \theta_0 \right)\right]
  \]
  where $W$ is a positive semi-definite matrix.
  The finite-sample distribution of $\widehat{\theta}$ is, in general, unknown, but by Theorem 2.2 of the paper
  \[
    \sqrt{n} \left( \widehat{\theta}_S - \theta_0\right) \rightarrow_d -K_S \Xi_S \left( M + \left[
    \begin{array}{c}
      0 \\ \tau
    \end{array}
  \right]\right) \equiv U_S
  \]
  where $M\sim N(0,\Omega)$ so we instead consider the \emph{asymptotic risk}
  \begin{align*}
    AR(\widehat{\theta}_S, W) &= E\left[ U_S' W U_S \right] = \mbox{trace}\left\{ E\left[ U_S U_S' \right]W \right\} \mbox{trace}\left\{W^{1/2} E\left[ U_S U_S' \right]W^{1/2} \right\}\\
    &= \mbox{trace}\left\{ W^{1/2}K_S \Xi_S 
      \left( \left[
      \begin{array}{cc}
        0 & 0 \\
        0 & \tau \tau'
      \end{array}
    \right] + \Omega\right)
    \Xi_S' K_S'W^{1/2} \right\}
  \end{align*}
  where $W^{1/2}$ is the (unique), symmetric, positive definite square root of $W$.
  To construct an asymptotically unbiased estimator of $AR(\widehat{\theta}_S, W)$ we substitute consistent estimators of $\Omega$ and $K_S$ and the asymptotically unbiased estimator of $\widehat{\tau}\widehat{\tau}'$ from Corollary 3.2 yielding
  \[
    \widehat{AR}\left( \widehat{\theta}_S, W \right) = 
    \mbox{trace}\left\{ W^{1/2}\widehat{K}_S \Xi_S 
      \left( \left[
      \begin{array}{cc}
        0 & 0 \\
        0 & \widehat{\tau}\widehat{\tau}' - \widehat{\Psi}\widehat{\Omega}\widehat{\Psi}
      \end{array}
    \right] + \Omega\right)
    \Xi_S' \widehat{K}_S'W^{1/2} \right\}
  \]
  which is nearly identical to the expression for the FMSC given in Equation 1 of the paper.
  The only difference is the presence of the weighting matrix $W$ and the trace operator in place of the vector of derivatives $\nabla_\theta\mu(\widehat{\theta})$.
  By minimizing $\widehat{AR}(\widehat{\theta}_S,W)$ over $S$ one can apply the same reasoning that underlies the FMSC to a more general class of quadratic risk functions.
  \todo[inline]{I think that when $W$ is diagonal, this is even simpler in that for any diagonal $W$ there's a corresponding ``target parameter'' $\mu$ that we can work in terms of without even changing the notation.
  Still need to think a bit more about the question of inference.
I think the solution is something like this.
If you are interested in two parameters, choose a $W$ that gives weight to them and only them.
Then there's no inconsistency in the inference since we're choosing a single specification. 
Could even get joint inference for the two using my simulation-based procedure I think.}

